Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-03-01 paperDistance/paper.tex
fiddling with dust

@@

>>>>

\usepackage{amsmath}

@@

The data are a transformation of the dust corrected absolute magnitude, and the dust corrected colors.

\begin{equation}
\label{eq:data}
\begin{aligned}
\mathrm{data vector} \;\;\;\; &\vec{y} = [10^{0.2M_{J,n}}, J_n - K_n] \;  n \in \mathrm{stars} \\
\mathrm{with \; absolute \; magnitude} \;\;\;\; &M_{J,n} = J_n - DM_n - Q_JE(B-V)_n \\
& DM_n = -5\mathrm{log_{10}}\frac{1}{\varpi} \\
\mathrm{and \; color} \;\;\;\; &J_n - K_n = J_n - K_n - Q_{JK}E(B-V)_n

\end{aligned}
\end{equation}

We fit the data using XD which maximizes the likelihood

\begin{equation}
\label{eq:xdlikelihood}
P(\vec{y}|\alpha, I)
\end{equation}

with the output mixture of gaussians

\begin{equation}
\label{eq:xd}
\begin{aligned}
\alpha = &\left\{\mathrm{amp}_k, \mu_k, V_k\right\}_{k=1}^K \; k \in \mathrm{Gaussians} \\
I = &\left\{\left\{\sigma^2_n\right\}_{n=1}^N, \mathrm{assumptions}\right\}
\end{aligned}
\end{equation}
